Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-07 paper.tex
Add comment on flow diagram
Add comment on referencing ongoing FCO work
tweak discussion of standard archetypes

The chosen scenario approximates a transition from a the current once-through light water
reactor (LWR) fleet to a full sodium fast reactor (SFR) fuel cycle within evaluation group 23 (EG-23)
in the DOE's Advanced Nuclear Fuel Cycle Options report
\cite{wigeland_nuclear_2014}. Scenario and transition details were patterned
after ongoing work by the DOE in their Fuel Cycle Options campaign.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.47\textwidth]{exp2/flow.eps}
    \caption[Material flow paths]{Potential material flow paths between facility types.}
    \label{fig:flow}
\end{figure}

A pre-release of Cyclus version 1.4 was used for this analysis.  Archetypes
used were the standard ones provided with Cyclus in the included Cycamore
library - also a pre-release of version 1.4.  A custom storage archetype was
used because Cycamore did not yet provide one.  The standard cycamore reactor archetype
was used for both LWR and SFR reactor types in cases MI and QI.  Correspondingly
the custom fleet-based reactor archetype described earlier was used for both reactor
types in cases MF and QF.  Additional configuration for the reactor types is
shown in Table \ref{tab:reactors} (cycle length includes the refueling outage).

>>>>

The chosen scenario approximates a transition from a the current once-through light water
reactor (LWR) fleet to a full sodium fast reactor (SFR) fuel cycle within evaluation group 23 (EG-23)
in the DOE's Advanced Nuclear Fuel Cycle Options report
\cite{wigeland_nuclear_2014}. Scenario and transition details were patterned
after ongoing work by the DOE in their Fuel Cycle Options campaign.
%% Not sure if we should make such an explicit reference to the ongoing FCO
%% transition work until they publish something. On one hand, it reveals
%% things they are secretive about. On the other hand, we should give them due
%% credit.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.47\textwidth]{exp2/flow.eps}
    \caption[Material flow paths]{Potential material flow paths between facility types.}
    %% consider a Cyclist-derived visualization here?
    \label{fig:flow}
\end{figure}

A pre-release of Cyclus version 1.4 was used for this analysis, with the
standard archetypes provided with Cyclus in the included Cycamore
library - also a pre-release of version 1.4.  A custom storage archetype was
developed because Cycamore did not yet provide one.  The standard cycamore reactor archetype
was used for both LWR and SFR reactor types in cases MI and QI.  Correspondingly
the custom fleet-based reactor archetype described earlier was used for both reactor
types in cases MF and QF.  Additional configuration for the reactor types is
shown in Table \ref{tab:reactors} (cycle length includes the refueling outage).
